---
title: "1_data_getting"
author: "Dave Lovell"
date: "17/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries1, message = FALSE, warning = FALSE}
library("dplyr")
library("magrittr")
library("here")
library("ggplot2")
library("forcats")
library("carutools") #devtools::install_github("davelovellCARU/carutools")
```

## Data Getting

Going to lead in the data. Note this is a static source - only gets updated when a human actor moves the fruit of [**portsmouthSurveyProcessing**](https://www.github.com/davelovellCARU/portsmouthSurveyProcessing) into the target dirctory.

Data is searched for in `O:\\` to begin with, as this is mostly likely to be up to date. If no `O:\\` connection exists, the internal `data` directory is checked. 

```{r lookForData}
### Directory / filename variables -----------------------------------------------
dataDir <- here::here("data")
oDataFile <- "O:/WCC/Learning and Development/Research/PROJECT - Portsmouth 2019 onwards/Data/leaders & attenders/attenders2018.rdat"
localDataFile<- paste0(dataDir, "/attenders2018.rdat")

### Look for the file in those places --------------------------------------------
if(file.exists(oDataFile)) {
  attenders <- readRDS(oDataFile)
  saveRDS(attenders, localDataFile)
  
} else if (file.exists(localDataFile)) {
  attenders <- readRDS(localDataFile)
  
} else stop("attenders2018.rdat not found. Try:
              - Establishing connection to the O drive OR
              - placing '2018attenders.rdat' in this repository's `data` directory")
```

## Data Examination

```{r lookAtNames}
names(attenders)
```

### Number of Responses

How many plants involved?

```{r plantIDLooking}
attenders %>% pull(plantId) %>% unique %>% length

attenders %>%
  group_by(plantId) %>% 
  summarise(totalResponses = n()) %>% 
  ungroup %>% 
  mutate(plantId = fct_reorder(plantId, totalResponses)) %T>% {
    # Make a barplot of this
    print(ggplot(.,aes(x = plantId, y = totalResponses)) +
    geom_bar(stat = "identity", fill = carutools::ca_orange()) +
    xlab("plants") + scale_x_discrete(breaks = NULL)) +
      ggtitle("Number of Responses from each Fresh Expression")
    } %T>% {
      # What's the mean number of responses?
      print(summarise(., mean(totalResponses)))
    } %T>% {
      # What's the median number of responses?
      attMedian <<- pull(summarise(., median(totalResponses)))
      print(summarise(., median(totalResponses)))
    } %>% {
      attMax <<- pull(summarise(., max(totalResponses)))
      print(summarise(., max(totalResponses)))
    } 
```

So an average of **`r attMedian`** people have completed from each church. But **`r attMax`** people from one fresh expression. I'm guessing it's Harbour. Let's check.

Ah can't check lol - don't have the names yet. Let's do that now:

No, wait - best practice would be to do that in the previous project. 

`Add_fxcNames_to_surveyProcessing.exe`

### Is it Harbour?

