---
title: "1_data_getting"
author: "Dave Lovell"
date: "17/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries1, message = FALSE, warning = FALSE}
library("dplyr")
library("magrittr")
library("here")
library("ggplot2")
library("forcats")
library("carutools") #devtools::install_github("davelovellCARU/carutools")
library("kableExtra")
library("patchwork")
```

## Data Getting

Going to lead in the data. Note this is a static source - only gets updated when a human actor moves the fruit of [**portsmouthSurveyProcessing**](https://www.github.com/davelovellCARU/portsmouthSurveyProcessing) into the target dirctory.

Data is searched for in `O:\\` to begin with, as this is mostly likely to be up to date. If no `O:\\` connection exists, the internal `data` directory is checked. 

```{r lookForData}
### Directory / filename variables -----------------------------------------------
dataDir <- here::here("data")
oDataFile <- "O:/WCC/Learning and Development/Research/PROJECT - Portsmouth 2019 onwards/Data/leaders & attenders/attenders2018.rdat"
localDataFile<- paste0(dataDir, "/attenders2018.rdat")

### Look for the file in those places --------------------------------------------
if(file.exists(oDataFile)) {
  attenders <- readRDS(oDataFile)
  saveRDS(attenders, localDataFile)
  
} else if (file.exists(localDataFile)) {
  attenders <- readRDS(localDataFile)
  
} else stop("attenders2018.rdat not found. Try:
              - Establishing connection to the O drive OR
              - placing '2018attenders.rdat' in this repository's `data` directory")
```

## Data Examination

```{r lookAtNames}
names(attenders)
```

### Number of Responses

How many plants involved?

```{r plantIDLooking, results = "asis"}
attenders %>% pull(plantId) %>% unique %>% length

attenders %>%
  group_by(plantId) %>% 
  summarise(totalResponses = n()) %>% 
  ungroup %>% 
  mutate(plantId = fct_reorder(plantId, totalResponses)) %T>% {
    # Make a barplot of this
    print(ggplot(.,aes(x = plantId, y = totalResponses)) +
    geom_bar(stat = "identity", fill = carutools::ca_orange()) +
    xlab("plants") + scale_x_discrete(breaks = NULL)) +
      ggtitle("Number of Responses from each Fresh Expression")
    } %T>% {
      # What's the mean number of responses?
      attMean <<- pull(summarise(., mean(totalResponses)))
      print(kable(summarise(., `Mean respondents` = mean(totalResponses))))
    } %T>% {
      # What's the median number of responses?
      attMedian <<- pull(summarise(., median(totalResponses)))
      print(kable(summarise(., `Median respondents` = median(totalResponses))))
    } %>% {
      attMax <<- pull(summarise(., max(totalResponses)))
      print(kable(summarise(., `Maximum Respondents` = max(totalResponses))))
    } 
```

So an average of **`r attMedian`** people have completed from each church. But **`r attMax`** people from one fresh expression. I'm guessing it's Harbour. Let's check.

Ah can't check lol - don't have the names yet. Let's do that now:

No, wait - best practice would be to do that in the previous project. 

`Add_fxcNames_to_surveyProcessing.exe`

### Is it Harbour?

```{r betYouItsHarbour, results = "asis"}
attenders %>% 
  group_by(plantId) %>% 
  summarise(fxcName = unique(fxcName),
            respondents = n()) %>% 
  filter(respondents == max(respondents)) %>% 
  select(-plantId) %>% 
  kable
```

Yes - knew it.

### Age distribution

#### See Under Fives

Would be good to know how many attenders are under five, as these will be included in some totals but excluded from most analysis.

Okay new question: Is it under fives or fives and under? Because other repos will need to change if the prior is true

```{r seeUnderFives}
underFiveSorted <-
  attenders %>% 
  mutate(`Over Five` = !(ageGroup %in% "0-5")) %>% 
  group_by(plantId, `Over Five`) %>% 
  summarise(`Total respondents` = n()) %>%
  ungroup %>% 
  mutate(plantId = fct_reorder(plantId, `Total respondents`))

Secondary <- unname(carutools::ca_secondary_cols())

overFiveBarPlot <- 
  ggplot(underFiveSorted,
         aes(x = plantId, y = `Total respondents`, fill = `Over Five`)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = rev(caruSecondary[1:2])) +
  scale_x_discrete(breaks = NULL) + xlab(NULL)

overFivePieChart <-
  ggplot(underFiveSorted %>% 
           group_by(`Over Five`) %>% 
           summarise(`Total respondents` = sum(`Total respondents`)),
         aes(x = 1, y = `Total respondents`, fill = `Over Five`)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = rev(caruSecondary[1:2])) +
  coord_polar(theta = "y") +
  xlab(NULL) + ylab(NULL) +
  scale_y_continuous(breaks = NULL) + 
  scale_x_continuous(breaks = NULL) +
  theme_minimal()

overFiveBarPlot + overFivePieChart

```